Taking Linear Logic Apart

### 2020-12-21 doc/paper/main.tex
replaced the footer on page 1
typos

\title{Taking Linear Logic Apart\\{\large Post-publication version: 2019-07-17}}
\author{%
  Wen Kokke
  \institute{University of Edinburgh\\ Edinburgh, Scotland}
  \email{wen.kokke@ed.ac.uk}
  \and
  Fabrizio Montesi
  \institute{University of Southern Denmark\\ Odense, Denmark}
  \email{fmontesi@imada.sdu.dk}
  \and
  Marco Peressotti
  \institute{University of Southern Denmark\\ Odense, Denmark}
  \email{peressotti@imada.sdu.dk}}
\def\titlerunning{Taking Linear Logic Apart}
\def\authorrunning{W.\ Kokke, F.\ Montesi, and M.\ Peressotti}

@@

The idea of using hypersequents to capture parallelism in linear logic judgements is not novel: Carbone \etal~\cite{carbone2018} extended the multiplicative-additive fragment of intuitionistic linear logic with hypersequents to type global descriptions of process communications known as choreographies. This work is distinct from our approach in that \hcp is based on classical linear logic and manipulates hypersequents differently: in Carbone \etal~\cite{carbone2018}, hypersequents can be formed only when sequents share resources (\cf \textsc{H-Mix}), and resource sharing is then tracked using an additional connection modality (which is not present in \hcp).
Montesi and Peressotti \cite{montesi2018} revisited \cp in the light of hypersequents to derive the first correspondence between the labelled transition system semantics on proof transformations, later refined in \cite{kokke2019}. The type system of \hcp is that of \cite{montesi2018} save for rule \textsc{H-Mix\textsubscript{0}} which is from \cite{kokke2019}. This is difference means that \cite{montesi2018} does not enjoy the translation to CLL that \hcp and \dhcp enjoy.

>>>>

\title{Taking Linear Logic Apart} %\\{\large Post-publication version: 2019-07-17}}
\author{%
  Wen Kokke
  \institute{University of Edinburgh\\ Edinburgh, Scotland}
  \email{wen.kokke@ed.ac.uk}
  \and
  Fabrizio Montesi
  \institute{University of Southern Denmark\\ Odense, Denmark}
  \email{fmontesi@imada.sdu.dk}
  \and
  Marco Peressotti
  \institute{University of Southern Denmark\\ Odense, Denmark}
  \email{peressotti@imada.sdu.dk}}
\def\titlerunning{Taking Linear Logic Apart}
\def\authorrunning{W.\ Kokke, F.\ Montesi, and M.\ Peressotti}

@@

The idea of using hypersequents to capture parallelism in linear logic judgements is not novel: Carbone \etal~\cite{carbone2018} extended the multiplicative-additive fragment of intuitionistic linear logic with hypersequents to type global descriptions of process communications known as choreographies. This work is distinct from our approach in that \hcp is based on classical linear logic and manipulates hypersequents differently: in Carbone \etal~\cite{carbone2018}, hypersequents can be formed only when sequents share resources (\cf \textsc{H-Mix}), and resource sharing is then tracked using an additional connection modality (which is not present in \hcp).
Montesi and Peressotti \cite{montesi2018} revisited \cp in the light of hypersequents to derive the first correspondence between the labelled transition system semantics and proof transformations, later refined in \cite{kokke2019}. The type system of \hcp is that of \cite{montesi2018} save for rule \textsc{H-Mix\textsubscript{0}} which is from \cite{kokke2019}. This difference means that \cite{montesi2018} does not enjoy the translation to CLL that \hcp and \dhcp enjoy.
